Different rules for binocular combination of luminance in cortical and subcortical pathways

### 2022-09-25 manuscript.Rmd
Minor bug fix

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping and modelling
# 3 - download all raw data and analyse (requires 48GB of storage)

@@

@@

levels <- unique(matchingdata$allref)
ratiosL <- c(1, 1, 1, 1, 1, 0.75, 0.5, 0.25, 0)
ratiosR <- c(0, 0.25, 0.5, 0.75, 1, 1, 1, 1, 1)
subjects <- unique(matchingdata$Participant)

>>>>

processdata <- 1  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping and modelling
# 3 - download all raw data and analyse (requires 48GB of storage)

@@

ratiosL <- c(1, 1, 1, 1, 1, 0.75, 0.5, 0.25, 0)
ratiosR <- c(0, 0.25, 0.5, 0.75, 1, 1, 1, 1, 1)

@@

levels <- unique(matchingdata$allref)
subjects <- unique(matchingdata$Participant)
